%------------------------
% Resume Template
% Author : Anubhav Singh
% Github : https://github.com/xprilion
% License : MIT
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemi}{}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Shubham Vij}} & Email: \href{mailto:}{reachme@shubhamvij.com}\\
  \textbf{{\large Senior Research Engineer at Snap Inc.}} & \href{https://www.linkedin.com/in/shubhamvij/}{LinkedIn} \\
  % \href{https://github.com/xprilion}{Github: ~~github.com/xprilion} \\
\end{tabular*}

\vspace{5pt}
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading{Snap Inc}{}
    {Senior Research Engineer}{August 2021 - Present}

    \vspace{-15pt}
    \resumeSubheading{}{}
    {Research Engineer}{September 2019 - August 2021}
    \vspace{5pt}

    Focus around engineering Artificial Intelligence / Machine Learning systems
to realize products out of Snap’s research. Through contributions at the lab,
have helped build solutions to train large scale graph neural networks and deduplicate news.

  \vspace{-10pt}
  \resumeSubheading{}{}
  {Software Engineer}{December 2018 - September 2019}
  \vspace{5pt}

  Engineered various key features for vertical video creation for Snap Publisher;
  some highlights include: optimizing video playback and html canvas
  performance, handling data management intricacies of distributed multi-tiered
  architecture, and introducing various new frameworks to ease development
  such as one for Generalized Message Passing for compute intensive webapps.

  \vspace{-10pt}
  \resumeSubheading{}{}
  {Research Engineer}{February 2018 - December 2018}
  \vspace{5pt}

  Maintained Research team's cloud compute tooling, used by 100s of ML
projects to scale up experiments; tangentially engineering tooling to improve
cost efficiency and cost reporting for the system.
Helped engineer foundations of multi-year research projects, including
Snapchat Trends - a subset of which, eventually became an external facing
product 3 years later.

\vspace{-10pt}
\resumeSubheading{}{}
{Software Engineer Intern}{Jan 2017 - April. 2017}
\vspace{5pt}

Designed a library for on-device offline keyword detection, which was later 
used as technology backing various speech recognition lenses.

\resumeSubheading{Amazon Inc}{}
{Software Development Engineer Intern}{May 2016 - August 2016}
\vspace{5pt}

Developed software to automate localization for the Amazon Silk browser,
saving roughly 1+ hour/week of manual engineering effort.

\resumeSubheading{IBM}{}
{Mobile Solutions Developer}{September 2015 - December 2015}
\vspace{5pt}

Consulted for one of the top 5 financial institutions in Canada, engineering
and presenting business and technical solutions centred around client
authentication to C-level executives. Worked with cross-company and crossorganizational teams to design and engineer POC for new authentication
architecture.

\resumeSubheading{Microsoft}{}
{Xbox Marketing Assistant}{January 2014 - April 2014}
\vspace{5pt}

Constructed analytical reports for games portfolio; automating parts of
the process by creating tools in VBA (Excel) to compute viability of rebate
programs by leveraging plethora of available signals (both internally and
externally) - derived insights were used for sales and inventory forecasting.
Designed and led a successful contextual digital marketing campaign for the
Canadian market, leveraging popular video game influencers, to drive demand
generation for launch of a new AAA game.



% \vspace{-5pt}
%     \resumeSubheading
% 		{DataCamp Inc.}{Remote}
% 		{Instructor (Part-time, Contractual)}{Dec 2018 -  Present}
% 		\resumeItemListStart
%         \resumeItem{Project Course - Find Movie Similarity from Plot Summaries}
%           {Created project based course using Unsupervised learning and natural language processing.}
%         \resumeItem{Tutorial - Introduction to Reinforcement Learning}
%           {Created tutorial for Q-learning RL algorithm and  concepts.}
%         \resumeItem{Impact}{Course has been taken by 250+ students so far with 4.65 average rating.}
% 		\resumeItemListEnd
\resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\vspace{-5pt}
\section{~~Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Waterloo}{Waterloo, ON}
      {Bachelors in Computer Science}{December. 2019}
    \resumeSubheading
      {Wilfrid Laurier University}{Waterloo, ON}
      {Bachelors in Business Administration}{December. 2019}
    %   \newline
    %   {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses:} Operating Systems, Data Structures, Analysis Of Algorithms, Artificial Intelligence, Machine Learning, Networking, Databases}}}
    \resumeSubHeadingListEnd
	    
\vspace{-5pt}
\section{Skills Summary}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{~~~Python, Java, Javascript, Objective-C, HTML, CSS}
	\resumeSubItem{We/Mobile}{~~React, Redux, Node, Express, iOS}
	\resumeSubItem{Tools}{~~~~~~~~~~~Bazel, Pytorch, Kubeflow, Monorepositories, Big Data, SQL, Machine Learning}
	\resumeSubItem{Platforms}{~~~~GCP, AWS}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\vspace{-5pt}
\section{Other Experience}
\resumeSubHeadingListStart

\resumeSubheading{Restuaraunt Inventory Management Software}{Self Employed}
{Owner}{September 2016 - August 2017}
\vspace{5pt}

Led a group of two other developers in engineering an inventory management software solution for 
small to medium sized restuaraunts.


\resumeSubheading{South African Embrace Foundation}{}
{Web Content Developer}{December 2015 - December 2016}
\vspace{5pt}

\resumeSubHeadingListEnd


% \vspace{-5pt}
% \section{Publications}
% \resumeSubHeadingListStart
% \resumeSubItem{Book: Deep Learning on Web (Web Development, Deep Learning)}{Work in Progress book to be published by Packt Publishing in late 2019. Tech: Django, Python, AWS, GCP, Azure (November '18)}
% \vspace{2pt}
% \resumeSubItem{Book: Deep Learning on Mobile Devices (Flutter App Development, Deep Learning)}{Work in Progress book to be published by Packt Publishing in late 2019. Tech: Flutter, Android, Firebase, TensorFlow, Python, Dart (December '18)}
% \resumeSubHeadingListEnd
% \vspace{-5pt}
% %-----------Awards-----------------
% \section{Honors and Awards}
% \begin{description}[font=$\bullet$]
% \item {Awarded title of Intel Software Innovator - May, 2019}
% \vspace{-5pt}
% \item {Second Runner's Up at TCS EngiNx Engineering Project Innovation Content - September, 2018 }
% \vspace{-5pt}
% \item {Runner's Up at Facebook Developers Circle Hackathon - August, 2017}

% \end{description}

% \vspace{-5pt}
% \section{Volunteer Experience}
%   \resumeSubHeadingListStart
% 	\resumeSubheading
%     {Community Lead at Developer Student Clubs NSEC}{Kolkata, India}
%     {Conducted online and offline technical \& soft-skills training impacting over 3000 students.}{Jan 2019 - Present}
% \vspace{5pt}
%     % \vspace{10pt}\textbf{\large{Community Experience}}
%     \resumeSubheading
%     {Event Organizer at Google Developers Group Kolkata}{Kolkata, India}
%     {Organized events, conducted workshops and delivered workshops reaching over 7000 developers.}{Jan 2018 - Present}

% \resumeSubHeadingListEnd

\end{document}